Versatile Robust Clustering of Ad Hoc Cognitive Radio Network

### 2016-12-06 journal-draft/bare_jrnl_comsoc.tex
modifying sec 2 and 3

\begin{theorem}
\label{theorem1}
Robust clustering problem in CRN is NP-hard, when the maximum size of clusters is larger than 3.
%Assume a CRN can be represented by a connected graph, and there is at least one common channel between any pair of neighbours, then forming at least two CR nodes into one cluster is NP-complete.
\end{theorem}
The proof is in Appendix~\ref{proof_theorem1}.
%This theorem actually indicates that the robust clustering problem in CRN is NP-hard.

With the definition of the robust clustering problem, we need to present this problem in the form of optimization to solve in the centralized manner.
The optimization is a binary linear programming problem as shown in~\ref{centralized_opt}.
%Binary linear programming problem is NP complement, but with the 
The result will be used as a comparison with the proposed distributed schemes. %looks for the solution which approaches to the global optimum, and the latter is the solution which is more suitable for the practical implementation.
%
%Exact cover problem can be solved with Knuth's Algorithm X~\cite{dancingLinks_Knuth} as it finds out all the instances of exact cover, then we can choose the one with the biggest sum of weights. 
%To make the formulation possible, we adopt heuristics in both the objective function and the constraints, besides, the objective is not totally aligned with the object in the Definition~\ref{def_centralized_clustering}.
%The problem by the Definition~\ref{def_centralized_clustering} is formulate

@@

The objective is to maximize the sum of the products of the size and the corresponding number of CCs of all the clusters.
We minimize the opposite of the real objective to make this problem solvable.
%
The variables of this problem are $x_{ij}$ where $i\in \{1,2,\cdots,G-1, G\}$ and $j\in \{1,2,\cdots,N-1, N\}$.
$N$ is the total number of CR users in network $\mathcal{N}$.
$G = |\mathcal{G}|$ and $\mathcal{G}$ is a collective of clusters in a CRN $\mathcal{N}$.
There is $\mathcal{G} \subseteq \mathcal{S}$, where $\mathcal{S}$ is the collection of all the possible clusters as described in Definition~\ref{def_centralized_clustering}.
%In practice, we can solve the problem with $\mathcal{G} = \mathcal{S}$ when $|\mathcal{S}|$ is not large. 
The subscript $i$ indicates the $i$th cluster in $\mathcal{G}$, and $j$ corresponds to the node ID of a CR node. 
$x_{ij}$ indicates whether the CR node $j$ resides in the $i$th potential cluster, \ie $x_{ij}=1$ means node $j$ resides in the cluster $C_i$. 
%
%Given a CRN $\mathcal{N}$ and desired cluster size $\delta$, we obtain a collection of clusters $\mathcal{G}$ which contains all the \textit{potential} clusters, and the sizes of these clusters are $1,2,\ldots,\delta$.
%Potential clusters are the clusters which satisfy the conditions introduced in Section~\ref{sec:model}. 
%Note that the potential clusters include the singleton ones.
%By permitting the existence of the singleton clusters, we can ensure that the $\mathcal{S}'$ in Definition~\ref{def_centralized_clustering} is always be feasible.
Based on the knowledge on $\mathcal{G}$, we construct a $G\times N$ matrix $Q_{G\text{x}N}$ which is shown in Figure~\ref{costant_matrix_Q}. 
Constant $q_{ij}$ is the element of $Q_{G\text{x}N}$, and its subscripts correspond to the $i$th cluster and CR node $j$ respectively.
$q_{ij}= |K(C_i)|$ when there is $j\in C_i$, and $q_{ij}= 0$ when there is $j\notin C_i$.
In other words, each non-zero element $q_{ij}$ means the number of CCs of the cluster $i$ where node $j$ resides.

@@

%
\section*{Proof of Theorem~\ref{theorem1}}
\label{proof_theorem1}
\begin{proof}
To prove the robust clustering problem is NP-hard, we reduce the \textit{maximum weighted k-set packing problem}, which is NP-hard when $k\geqslant 3$~\cite{Computers_a_Intractability}, to the the robust clustering problem to show the latter is at least as hard as the former.
Given a collection of sets of cardinality at most $k$ with weights for each set, the maximum weighted packing problem is that of finding a collection of disjoint sets of maximum total weight.
The decision version of weighted $k$-set packing problem is,
\begin{mydef}
\label{def_kset_packing}
Given a finite set $\mathcal{G}$ of non-negative integers where $\mathcal{G} \subsetneq \mathbb{N}$, and a collection of sets $\mathcal{Q}=\{S_1,S_2,\cdots,S_m\}$ where $S_i \subseteq \mathcal{G}$ for $1 \leq i \leq m$, every set $S$ in $\mathcal{Q}$ has a weight $\omega(S) \in \mathbb{R}$.
%
The problem is to find a collection $\mathcal{S} \subseteq \mathcal{Q}$ such that $\mathcal{S}$ contains only pairwise disjoint sets and the total weight of the sets in $\mathcal{S}$ is greater than a given positive number $\lambda$, i.e., $\sum_{S \in \mathcal{S}} \omega(S) > \lambda$.
\end{mydef}

>>>>

\begin{theorem}
\label{theorem1}
Robust clustering problem in CRN is NP-hard, when the maximum size of clusters is larger than 3, and $\delta_1=1$ and $\delta_2 = N$ .
%Assume a CRN can be represented by a connected graph, and there is at least one common channel between any pair of neighbours, then forming at least two CR nodes into one cluster is NP-complete.
\end{theorem}
The proof is in Appendix~\ref{proof_theorem1}.
%This theorem actually indicates that the robust clustering problem in CRN is NP-hard.

With the definition of the robust clustering problem, we need to present this problem in the form of optimization to solve in the centralized manner.
The optimization is a binary linear programming problem as shown in~\ref{centralized_opt}.
%Binary linear programming problem is NP complement, but with the 
%The result will be used as a comparison with the proposed distributed schemes. %looks for the solution which approaches to the global optimum, and the latter is the solution which is more suitable for the practical implementation.
%
%Exact cover problem can be solved with Knuth's Algorithm X~\cite{dancingLinks_Knuth} as it finds out all the instances of exact cover, then we can choose the one with the biggest sum of weights. 
%To make the formulation possible, we adopt heuristics in both the objective function and the constraints, besides, the objective is not totally aligned with the object in the Definition~\ref{def_centralized_clustering}.
%The problem by the Definition~\ref{def_centralized_clustering} is formulate

@@

The objective is to maximize the sum of CCs of all the clusters.
We minimize the opposite of the real objective to make this problem solvable.
%
The variables of this problem are $x_{ij}$ where $i\in \{1,2,\cdots,G-1, G\}$ and $j\in \{1,2,\cdots,N-1, N\}$.
$N$ is the total number of CR users in network $\mathcal{N}$.
$G = |\mathcal{G}|$ and $\mathcal{G}$ is a collective of clusters in a CRN $\mathcal{N}$.
There is $\mathcal{G} \subseteq \mathcal{S}$, where $\mathcal{S}$ is the collection of all the possible clusters as described in Definition~\ref{def_centralized_clustering}.
%In practice, we can solve the problem with $\mathcal{G} = \mathcal{S}$ when $|\mathcal{S}|$ is not large. 
The subscript $i$ indicates the $i$th cluster in $\mathcal{G}$, and $j$ corresponds to the node ID of a CR node. 
$x_{ij}$ indicates whether the CR node $j$ resides in the $i$th potential cluster, \ie $x_{ij}=1$ means node $j$ resides in the cluster $C_i$. 
%
%Given a CRN $\mathcal{N}$ and desired cluster size $\delta$, we obtain a collection of clusters $\mathcal{G}$ which contains all the \textit{potential} clusters, and the sizes of these clusters are $1,2,\ldots,\delta$.
%Potential clusters are the clusters which satisfy the conditions introduced in Section~\ref{sec:model}. 
%Note that the potential clusters include the singleton ones.
%By permitting the existence of the singleton clusters, we can ensure that the $\mathcal{S}'$ in Definition~\ref{def_centralized_clustering} is always be feasible.
Based on the knowledge on $\mathcal{G}$, we construct a $G\times N$ matrix $Q_{G\text{x}N}$ which is shown in Figure~\ref{costant_matrix_Q}. 
Constant $q_{ij}$ is the element of $Q_{G\text{x}N}$, and its subscripts correspond to the $i$th cluster and CR node $j$ respectively.
$q_{ij}= |K(C_i)|$ when there is $j\in C_i$, and $q_{ij}= 0$ when there is $j\notin C_i$.
In other words, each non-zero element $q_{ij}$ means the number of CCs of the cluster $i$ where node $j$ resides.

@@

%
\section*{Proof of Theorem~\ref{theorem1}}
\label{proof_theorem1}
\begin{proof}
To prove the robust clustering problem is NP-hard, we reduce the \textit{maximum weighted k-set packing problem}, which is NP-hard when $k\geqslant 3$~\cite{Computers_a_Intractability}, to the the robust clustering problem to show the latter is at least as hard as the former.
Given a collection of sets of cardinality at most $k$ with weights for each set, the maximum weighted packing problem is that of finding a collection of disjoint sets of maximum total weight.
The decision version of weighted $k$-set packing problem is,
\begin{mydef}
\label{def_kset_packing}
Given a finite set $\mathcal{G}$ of non-negative integers where $\mathcal{G} \subsetneq \mathbb{N}$, and a collection of sets $\mathcal{Q}=\{S_1,S_2,\cdots,S_m\}$ where $S_i \subseteq \mathcal{G}$ and $\max(S_i)\geq 3$ for $1 \leq i \leq m$.
Every set $S$ in $\mathcal{Q}$ has a weight $\omega(S) \in \mathbb{R}$. 
%
The problem is to find a collection $\mathcal{S} \subseteq \mathcal{Q}$ such that $\mathcal{S}$ contains only pairwise disjoint sets and the total weight of the sets in $\mathcal{S}$ is greater than a given positive number $\lambda$, i.e., $\sum_{S \in \mathcal{S}} \omega(S) > \lambda$.
\end{mydef}
